A Large-Scale Study of the Use of Eval in R

### 2020-08-23 inst/paper/main.tex
Fix
Add run data

The core R packages are the biggest consumers of eval. Majority of calls,
\CoreAllCallCountRnd, originate from the core R packages. Kaggle code, which is
end-user code, has merely \AllKaggleCallCountRnd calls to eval.

@@

>>>>

The core R packages are the biggest consumers of eval. Majority of calls,
\CoreAllCallCountRnd, originate from the core R packages. Kaggle code, which is
end-user code, has merely \KaggleAllCallCountRnd calls to eval.

@@

All the \TotalFileCount files in our corpus call eval. \CoreEvalFileCount
(\CoreEvalFilePerc) call only core evals, \AllEvalFileCount (\AllEvalFilePerc)
call both package and core evals; and, \PackageEvalFileCount
(\PackageEvalFilePerc) call only package evals. Of the \AllEvalFileCount
(\AllEvalFilePerc) files that call both package and base eval,
\EightyCoreEvalFilePerc (\EightyCoreEvalFileCount) files make over 80\% eval
calls to core evals.
